Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2015-04-09 Paper.tex
Correct ranges for ECDSA privkey and signature r, s values

It is assumed that the sender has a valid private key $p_r$, a randomly selected positive integer in the range $(0, 2^{256})$ represented as a byte array of length 32 in big-endian form.

@@

Where $p_u$ is the public key, assumed to be a byte array of size 64 (formed from the concatenation of two positive integers each $< 2^{256}$) and $p_r$ is the private key, a byte array of size 32 (or a single positive integer $< 2^{256}$). It is assumed that $v$ is the `recovery id', a 1 byte value specifying the sign and finiteness of the curve point; this value is in the range of $[27, 30]$, however we declare the upper two possibilities, representing infinite values, invalid.

We declare that a signature is invalid unless the following is true:
\begin{equation}
v \in \{27,28\} \quad\wedge\quad r < \mathtt{\tiny secp256k1n} \quad\wedge\quad s < \mathtt{\tiny secp256k1p}
\end{equation}

where:
\begin{eqnarray}
\mathtt{\tiny secp256k1n} &=& 115792089237316195423570985008687907852837564279074904382605163141518161494337\\
\mathtt{\tiny secp256k1p} &=& 2^{256} - 2^{32} - 977\\
\end{eqnarray}

>>>>

It is assumed that the sender has a valid private key $p_r$, a randomly selected positive integer
% to avoid line break in range definition

in the range $(1, \mathtt{\tiny secp256k1n} - 1)$ represented as a byte array of length 32 in big-endian form.

@@

Where $p_u$ is the public key, assumed to be a byte array of size 64 (formed from the concatenation of two positive integers each $< 2^{256}$) and $p_r$ is the private key, a byte array of size 32 (or a single positive integer in the aforementioned range). It is assumed that $v$ is the `recovery id', a 1 byte value specifying the sign and finiteness of the curve point; this value is in the range of $[27, 30]$, however we declare the upper two possibilities, representing infinite values, invalid.

We declare that a signature is invalid unless the following is true:
\begin{eqnarray}
0 < r < \mathtt{\tiny secp256k1n} \quad\wedge\quad \\
0 < s < \mathtt{\tiny secp256k1n} \quad\wedge\quad \\
v \in \{27,28\}
\end{eqnarray}

where:
\begin{eqnarray}
\mathtt{\tiny secp256k1n} &=& 115792089237316195423570985008687907852837564279074904382605163141518161494337
%\mathtt{\tiny secp256k1p} &=& 2^{256} - 2^{32} - 977\\
\end{eqnarray}
